---
title: "Hospital Survey Data Analysis"
author: "Đam Mê Nghiên Cứu"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
---

```{r, include = F, warning =F}
library(flextable)
library(performance)
library(pacman)
p_load(forcats)
```

```{r, include = FALSE}
knitr:: opts_chunk$set(echo = FALSE, warning = FALSE, mesage = FALSE, comment = "##", 
                       dpi = 4*72, fig.width = 8.5, fig.height = 4.5)
``` 

```{r setup cool, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r run_data_preparation, include = FALSE}
# Run the data preparation script
rmarkdown::render("prepare_raw_data.Rmd")
```

# Table 1: Baseline Demographic Characteristics
```{r create_baseline_table}
# Create baseline characteristics table
baseline_table <- data1_processed %>%
  select(
    age,
    age_category,
    A2_gender,
    A4_education_level,
    A5_marital_status,
    A6_living_situation,
    A7_occupation_cleaned,
    A8_monthly_income,
    A9_payment_method,
    A10_hospital_treated,
    A11_1_clinical_department_cleaned,
    A12_0_admission_reason_code,
    length_of_stay_clean,
    A14_other_chronic_disease,
    A15_health_insurance,
    A16_used_insurance_for_payment,
    A17_discharge_condition,
    A18_physical_health_perception,
    A19_mental_health_perception,
    C1_overall_hospital_experience_score
  ) %>%
  tbl_summary(
    by = age_category,
    label = list(
      age ~ "Age (years)",
      A2_gender ~ "A2 - Gender",
      A4_education_level ~ "A4 - Education Level", 
      A5_marital_status ~ "A5 - Marital Status",
      A6_living_situation ~ "A6 - Living Situation",
      A7_occupation_cleaned ~ "A7 - Occupation",
      A8_monthly_income ~ "A8 - Monthly Income",
      A9_payment_method ~ "A9 - Payment Method",
      A10_hospital_treated ~ "A10 - Hospital",
      A11_1_clinical_department_cleaned ~ "A11 - Department",
      A12_0_admission_reason_code ~ "A12 - Admission Reason",
      length_of_stay_clean ~ "Length of Stay (days)",
      A14_other_chronic_disease ~ "A14 - Other Chronic Disease",
      A15_health_insurance ~ "A15 - Health Insurance",
      A16_used_insurance_for_payment ~ "A16 - Used Insurance for Payment",
      A17_discharge_condition ~ "A17 - Discharge Condition",
      A18_physical_health_perception ~ "A18 - Physical Health Perception",
      A19_mental_health_perception ~ "A19 - Mental Health Perception",
      C1_overall_hospital_experience_score ~ "C1 - Overall Experience Score (0-10)"
    ),
    statistic = list(
      all_continuous() ~ "{median} ({p25}, {p75})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    missing_text = "Missing",
    type = list(
      C1_overall_hospital_experience_score ~ "continuous"
    )
  ) %>%
  add_overall() %>%
  bold_labels() %>%
  modify_header(
    label = "**Characteristic**",
    stat_0 = "**Overall**\nN = {N}"
  ) %>%
  modify_spanning_header(c("stat_1", "stat_2", "stat_3", "stat_4") ~ "**Age Group**")

# Convert to gt table with styling
final_table <- baseline_table %>%
  as_gt() %>%
  tab_options(
    table.font.names = "Arial",
    table.font.size = 11,
    row.striping.background_color = "#F8F9FA",
    table.border.top.style = "solid",
    table.border.top.width = px(2),
    table.border.top.color = "black",
    table.border.bottom.style = "solid", 
    table.border.bottom.width = px(2),
    table.border.bottom.color = "black",
    column_labels.border.top.style = "solid",
    column_labels.border.top.width = px(2),
    column_labels.border.top.color = "black",
    column_labels.border.bottom.style = "solid",
    column_labels.border.bottom.width = px(1),
    column_labels.border.bottom.color = "black"
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_title()
  ) %>%
  tab_footnote(
    footnote = "Data presented as median (IQR) for continuous variables and n (%) for categorical variables.",
    locations = cells_title()
  )
```

```{r display_table}
final_table
```

\pagebreak
# Table 1: Adjusted Odds Ratios for Positive Hospital Experience - Core Communication Model

```{r model1_fit}
# Filter data for complete cases in Model 1 variables
model1_data <- data1_processed %>%
  filter(!is.na(c1_overall_experience_binary),
         !is.na(B1_doctor_clear_answers),
         !is.na(B2_nurse_clear_answers), 
         !is.na(B4_doctor_clear_communication),
         !is.na(B8_respectful_treatment_by_staff))

# Model 1: Core Communication Model
model1 <- glm(c1_overall_experience_binary ~ 
              B1_doctor_clear_answers + 
                B2_nurse_clear_answers + 
                B3_consistent_staff_answers + 
                B4_doctor_clear_communication + 
                B5_doctor_anxiety_counseling + 
                B6_nurse_anxiety_counseling + 
                B7_want_treatment_decision_participation + 
                B8_respectful_treatment_by_staff +
                B9_shared_concerns_with_staff + 
                B10_experienced_pain + 
                B10_1_staff_helped_pain_control +
                B11_family_communication_with_doctor + 
                B12_family_received_recovery_information + 
                B13_clear_medication_instructions + 
                B14_medication_side_effects_explained + 
                B15_warning_signs_explained, 
              family = binomial, 
              data = model1_data)

# Create professional flextable for Model 1
model1_table <- tbl_regression(
  model1,
  exponentiate = TRUE,
  label = list(
    B1_doctor_clear_answers ~ "B1 - Doctor clear answers",
    B2_nurse_clear_answers ~ "B2 - Nurse clear answers", 
    B4_doctor_clear_communication ~ "B4 - Doctor clear communication",
    B8_respectful_treatment_by_staff ~ "B8 - Respectful treatment by staff", 
    B3_consistent_staff_answers ~ "B3 - Consistent staff answers ", 
    B4_doctor_clear_communication ~ "B4 - Doctor clear communication", 
    B5_doctor_anxiety_counseling ~ "B5 - Doctor anxiety counseling", 
    B6_nurse_anxiety_counseling ~ "B6 - Nurse anxiety counseling", 
    B7_want_treatment_decision_participation ~"B7 - Treatment decision participation", 
    B8_respectful_treatment_by_staff ~ "B8 - Respectful treatment by staff", 
    B9_shared_concerns_with_staff ~ "B9 - Shared concerns with staff", 
    B10_experienced_pain ~ "B10 - Experienced pain", 
    B10_1_staff_helped_pain_control ~ "B10_1 - Staff helped pain control", 
    B11_family_communication_with_doctor ~ "B11 - Family communication with doctor", 
    B12_family_received_recovery_information ~ "B12 - Family received recovery information", 
    B13_clear_medication_instructions ~ "B13 - Clear medication instructions", 
    B14_medication_side_effects_explained ~ "B14 - Medication side effects explained", 
    B15_warning_signs_explained ~ "B15 - Warning signs explained"),
  estimate_fun = function(x) style_ratio(x, digits = 3),
  pvalue_fun = function(x) style_pvalue(x, digits = 3)
) %>%
  bold_p(t = 0.05) %>%
  modify_header(
    label = "**Variable**",
    estimate = "**Adjusted OR**", 
    ci = "**95% CI**",
    p.value = "**p-value**"
  )

# Convert to flextable with professional styling
model1_flex <- model1_table %>%
  as_flex_table() %>%
  theme_vanilla() %>%
  bg(part = "header", bg = "#D9D9D9") %>%
  color(part = "header", color = "black") %>%
  bold(part = "header") %>%
  align(part = "header", align = "center") %>%
  align(j = c("estimate", "ci", "p.value"), align = "center", part = "body") %>%
  align(j = "label", align = "left", part = "body") %>%
  bg(i = seq(2, nrow(model1_table$table_body), by = 2), bg = "#F2F2F2", part = "body") %>%
  width(j = "label", width = 2.8) %>%
  width(j = "estimate", width = 1.0) %>%
  width(j = "ci", width = 1.5) %>%
  width(j = "p.value", width = 1.0) %>%
  add_footer_lines(paste0("OR = Odds Ratio; CI = Confidence Interval; N = ", nobs(model1))) %>%
  fontsize(part = "footer", size = 9) %>%
  italic(part = "footer") %>%
  autofit()

model1_flex
```

\pagebreak

# Table 2: Adjusted Odds Ratios for Positive Hospital Experience - Enhanced Model with Patient Characteristics

```{r model_2 with some characteristic}
# Filter data for complete cases in Model 2 variables
model2_data <- data1_processed %>%
  filter(!is.na(c1_overall_experience_binary),
         !is.na(B1_doctor_clear_answers),
         !is.na(B2_nurse_clear_answers), 
         !is.na(B4_doctor_clear_communication),
         !is.na(B8_respectful_treatment_by_staff),
         !is.na(age_category),
         !is.na(A2_gender),
         !is.na(length_of_stay_clean),
         !is.na(A14_other_chronic_disease),
         !is.na(A17_discharge_condition))

# Model 2: Core Communication + Patient Characteristics
model2 <- glm(c1_overall_experience_binary ~ 
              B1_doctor_clear_answers + 
              B2_nurse_clear_answers + 
              B4_doctor_clear_communication + 
              B8_respectful_treatment_by_staff +
              age_category + 
              A2_gender + 
              length_of_stay_clean + 
              A14_other_chronic_disease + 
              A17_discharge_condition,
              family = binomial, 
              data = model2_data)

# Create professional flextable for Model 2
model2_table <- tbl_regression(
  model2,
  exponentiate = TRUE,
  label = list(
    B1_doctor_clear_answers ~ "B1 - Doctor clear answers",
    B2_nurse_clear_answers ~ "B2 - Nurse clear answers", 
    B4_doctor_clear_communication ~ "B4 - Doctor clear communication",
    B8_respectful_treatment_by_staff ~ "B8 - Respectful treatment by staff",
    age_category ~ "Age category",
    A2_gender ~ "A2 - Gender",
    length_of_stay_clean ~ "Length of stay (per day)",
    A14_other_chronic_disease ~ "A14 - Other chronic disease",
    A17_discharge_condition ~ "A17 - Discharge condition"
  ),
  estimate_fun = function(x) style_ratio(x, digits = 3),
  pvalue_fun = function(x) style_pvalue(x, digits = 3)
) %>%
  bold_p(t = 0.05) %>%
  modify_header(
    label = "**Variable**",
    estimate = "**Adjusted OR**", 
    ci = "**95% CI**",
    p.value = "**p-value**"
  )

# Convert to flextable with professional styling
model2_flex <- model2_table %>%
  as_flex_table() %>%
  theme_vanilla() %>%
  bg(part = "header", bg = "#D9D9D9") %>%
  color(part = "header", color = "black") %>%
  bold(part = "header") %>%
  align(part = "header", align = "center") %>%
  align(j = c("estimate", "ci", "p.value"), align = "center", part = "body") %>%
  align(j = "label", align = "left", part = "body") %>%
  bg(i = seq(2, nrow(model2_table$table_body), by = 2), bg = "#F2F2F2", part = "body") %>%
  width(j = "label", width = 2.8) %>%
  width(j = "estimate", width = 1.0) %>%
  width(j = "ci", width = 1.5) %>%
  width(j = "p.value", width = 1.0) %>%
  add_footer_lines(paste0("OR = Odds Ratio; CI = Confidence Interval; N = ", nobs(model2))) %>%
  fontsize(part = "footer", size = 9) %>%
  italic(part = "footer") %>%
  width(j = 1, width = 2.8) %>%
  width(j = 2, width = 1.0) %>% 
  width(j = 3, width = 1.5) %>%
  width(j = 4, width = 1.0)

model2_flex
```

\pagebreak

# Table 3: Adjusted Odds Ratios for Positive Hospital Experience - Complete Model with All Patient Experience Variables

```{r}
# Filter data for complete cases in Model 3 variables
model3_data <- data1_processed %>%
  filter(!is.na(c1_overall_experience_binary),
         !is.na(B1_doctor_clear_answers),
         !is.na(B2_nurse_clear_answers),
         !is.na(B3_consistent_staff_answers),
         !is.na(B4_doctor_clear_communication),
         !is.na(B5_doctor_anxiety_counseling),
         !is.na(B6_nurse_anxiety_counseling),
         !is.na(B8_respectful_treatment_by_staff),
         !is.na(B10_experienced_pain),
         !is.na(B13_clear_medication_instructions),
         !is.na(B14_medication_side_effects_explained),
         !is.na(B15_warning_signs_explained),
         !is.na(age_category),
         !is.na(A2_gender),
         !is.na(length_of_stay_clean),
         !is.na(A14_other_chronic_disease),
         !is.na(A17_discharge_condition),
         !is.na(A11_1_clinical_department_cleaned))

# Model 3: Full Model with All B Variables + Patient Characteristics
model3 <- glm(c1_overall_experience_binary ~ 
              B1_doctor_clear_answers + 
              B2_nurse_clear_answers + 
              B3_consistent_staff_answers + 
              B4_doctor_clear_communication + 
              B5_doctor_anxiety_counseling + 
              B6_nurse_anxiety_counseling +
              B8_respectful_treatment_by_staff + 
              B10_experienced_pain +
              B13_clear_medication_instructions + 
              B14_medication_side_effects_explained +
              B15_warning_signs_explained +
              age_category + 
              A2_gender + 
              length_of_stay_clean + 
              A14_other_chronic_disease + 
              A17_discharge_condition +
              A11_1_clinical_department_cleaned,
              family = binomial, 
              data = model3_data)

# Create professional flextable for Model 3
model3_table <- tbl_regression(
  model3,
  exponentiate = TRUE,
  label = list(
    B1_doctor_clear_answers ~ "B1 - Doctor clear answers",
    B2_nurse_clear_answers ~ "B2 - Nurse clear answers",
    B3_consistent_staff_answers ~ "B3 - Consistent staff answers",
    B4_doctor_clear_communication ~ "B4 - Doctor clear communication",
    B5_doctor_anxiety_counseling ~ "B5 - Doctor anxiety counseling",
    B6_nurse_anxiety_counseling ~ "B6 - Nurse anxiety counseling",
    B8_respectful_treatment_by_staff ~ "B8 - Respectful treatment by staff",
    B10_experienced_pain ~ "B10 - Experienced pain",
    B13_clear_medication_instructions ~ "B13 - Clear medication instructions",
    B14_medication_side_effects_explained ~ "B14 - Medication side effects explained",
    B15_warning_signs_explained ~ "B15 - Warning signs explained",
    age_category ~ "Age category",
    A2_gender ~ "A2 - Gender",
    length_of_stay_clean ~ "Length of stay (per day)",
    A14_other_chronic_disease ~ "A14 - Other chronic disease",
    A17_discharge_condition ~ "A17 - Discharge condition",
    A11_1_clinical_department_cleaned ~ "A11 - Clinical department"
  ),
  estimate_fun = function(x) style_ratio(x, digits = 3),
  pvalue_fun = function(x) style_pvalue(x, digits = 3)
) %>%
  bold_p(t = 0.05) %>%
  modify_header(
    label = "**Variable**",
    estimate = "**Adjusted OR**", 
    ci = "**95% CI**",
    p.value = "**p-value**"
  )

# Convert to flextable with professional styling
model3_flex <- model3_table %>%
  as_flex_table() %>%
  theme_vanilla() %>%
  bg(part = "header", bg = "#D9D9D9") %>%
  color(part = "header", color = "black") %>%
  bold(part = "header") %>%
  align(part = "header", align = "center") %>%
  align(j = c("estimate", "ci", "p.value"), align = "center", part = "body") %>%
  align(j = "label", align = "left", part = "body") %>%
  bg(i = seq(2, nrow(model3_table$table_body), by = 2), bg = "#F2F2F2", part = "body") %>%
  width(j = "label", width = 2.8) %>%
  width(j = "estimate", width = 1.0) %>%
  width(j = "ci", width = 1.5) %>%
  width(j = "p.value", width = 1.0) %>%
  add_footer_lines(paste0("OR = Odds Ratio; CI = Confidence Interval; N = ", nobs(model3))) %>%
  fontsize(part = "footer", size = 9) %>%
  italic(part = "footer") %>%
  width(j = 1, width = 2.8) %>%
  width(j = 2, width = 1.0) %>% 
  width(j = 3, width = 1.5) %>%
  width(j = 4, width = 1.0)

model3_flex
```
```{r}
check_model(model3)
```

# Same predictor as Model 3, but change response variable to continuous outcome (C1_overall_hospital_experience_score)

```{r}
# Filter data for complete cases in Model 4 variables (using continuous outcome)
model4_data <- data1_processed %>%
  filter(!is.na(C1_overall_hospital_experience_score),
         !is.na(B1_doctor_clear_answers),
         !is.na(B2_nurse_clear_answers),
         !is.na(B3_consistent_staff_answers),
         !is.na(B4_doctor_clear_communication),
         !is.na(B5_doctor_anxiety_counseling),
         !is.na(B6_nurse_anxiety_counseling),
         !is.na(B8_respectful_treatment_by_staff),
         !is.na(B10_experienced_pain),
         !is.na(B13_clear_medication_instructions),
         !is.na(B14_medication_side_effects_explained),
         !is.na(B15_warning_signs_explained),
         !is.na(age_category),
         !is.na(A2_gender),
         !is.na(length_of_stay_clean),
         !is.na(A14_other_chronic_disease),
         !is.na(A17_discharge_condition),
         !is.na(A11_1_clinical_department_cleaned))

# Model 4: Linear Regression with Continuous Overall Experience Score
model4 <- lm(C1_overall_hospital_experience_score ~ 
             B1_doctor_clear_answers + 
             B2_nurse_clear_answers + 
             B3_consistent_staff_answers + 
             B4_doctor_clear_communication + 
             B5_doctor_anxiety_counseling + 
             B6_nurse_anxiety_counseling +
             B8_respectful_treatment_by_staff + 
             B10_experienced_pain +
             B13_clear_medication_instructions + 
             B14_medication_side_effects_explained +
             B15_warning_signs_explained +
             age_category + 
             A2_gender + 
             length_of_stay_clean + 
             A14_other_chronic_disease + 
             A17_discharge_condition +
             A11_1_clinical_department_cleaned,
             data = model4_data)

# Create professional flextable for Model 4
model4_table <- tbl_regression(
  model4,
  label = list(
    B1_doctor_clear_answers ~ "B1 - Doctor clear answers",
    B2_nurse_clear_answers ~ "B2 - Nurse clear answers",
    B3_consistent_staff_answers ~ "B3 - Consistent staff answers",
    B4_doctor_clear_communication ~ "B4 - Doctor clear communication",
    B5_doctor_anxiety_counseling ~ "B5 - Doctor anxiety counseling",
    B6_nurse_anxiety_counseling ~ "B6 - Nurse anxiety counseling",
    B8_respectful_treatment_by_staff ~ "B8 - Respectful treatment by staff",
    B10_experienced_pain ~ "B10 - Experienced pain",
    B13_clear_medication_instructions ~ "B13 - Clear medication instructions",
    B14_medication_side_effects_explained ~ "B14 - Medication side effects explained",
    B15_warning_signs_explained ~ "B15 - Warning signs explained",
    age_category ~ "Age category",
    A2_gender ~ "A2 - Gender",
    length_of_stay_clean ~ "Length of stay (per day)",
    A14_other_chronic_disease ~ "A14 - Other chronic disease",
    A17_discharge_condition ~ "A17 - Discharge condition",
    A11_1_clinical_department_cleaned ~ "A11 - Clinical department"
  ),
  estimate_fun = function(x) style_number(x, digits = 3),
  pvalue_fun = function(x) style_pvalue(x, digits = 3)
) %>%
  bold_p(t = 0.05) %>%
  modify_header(
    label = "**Variable**",
    estimate = "**Beta Coefficient**", 
    ci = "**95% CI**",
    p.value = "**p-value**"
  )

# Convert to flextable with professional styling
model4_flex <- model4_table %>%
  as_flex_table() %>%
  theme_vanilla() %>%
  bg(part = "header", bg = "#D9D9D9") %>%
  color(part = "header", color = "black") %>%
  bold(part = "header") %>%
  align(part = "header", align = "center") %>%
  align(j = c("estimate", "ci", "p.value"), align = "center", part = "body") %>%
  align(j = "label", align = "left", part = "body") %>%
  bg(i = seq(2, nrow(model4_table$table_body), by = 2), bg = "#F2F2F2", part = "body") %>%
  width(j = "label", width = 2.8) %>%
  width(j = "estimate", width = 1.2) %>%
  width(j = "ci", width = 1.5) %>%
  width(j = "p.value", width = 1.0) %>%
  add_footer_lines(paste0("Beta = Regression Coefficient; CI = Confidence Interval; N = ", nobs(model4), 
                          "; R² = ", round(summary(model4)$r.squared, 3))) %>%
  fontsize(part = "footer", size = 9) %>%
  italic(part = "footer") %>%
  width(j = 1, width = 2.8) %>%
  width(j = 2, width = 1.2) %>% 
  width(j = 3, width = 1.5) %>%
  width(j = 4, width = 1.0)

model4_flex
```

```{r}
library(MASS)
# Fit the full model 
full.model <- lm(C1_overall_hospital_experience_score ~ B1_doctor_clear_answers + 
             B2_nurse_clear_answers + 
             B3_consistent_staff_answers + 
             B4_doctor_clear_communication + 
             B5_doctor_anxiety_counseling + 
             B6_nurse_anxiety_counseling +
             B8_respectful_treatment_by_staff + 
             B10_experienced_pain +
             B13_clear_medication_instructions + 
             B14_medication_side_effects_explained +
             B15_warning_signs_explained +
             age_category + 
             A2_gender + 
             length_of_stay_clean + 
             A14_other_chronic_disease + 
             A17_discharge_condition +
             A11_1_clinical_department_cleaned, data = data1_processed)

# Stepwise regression model
step.model <- stepAIC(full.model, direction = "both", 
                      trace = FALSE)
summary(step.model)

```

```{r, eval = FALSE}
models <- regsubsets(C1_overall_hospital_experience_score ~ B1_doctor_clear_answers + 
             B2_nurse_clear_answers + 
             B3_consistent_staff_answers + 
             B4_doctor_clear_communication + 
             B5_doctor_anxiety_counseling + 
             B6_nurse_anxiety_counseling +
             B8_respectful_treatment_by_staff + 
             B10_experienced_pain +
             B13_clear_medication_instructions + 
             B14_medication_side_effects_explained +
             B15_warning_signs_explained +
             age_category + 
             A2_gender + 
             length_of_stay_clean + 
             A14_other_chronic_disease + 
             A17_discharge_condition +
             A11_1_clinical_department_cleaned, data = data1_processed, nvmax = 5,
                     method = "seqrep")
summary(models)
```

```{r, eval = FALSE}
# Initialize a model with all predictors
both_model <- lm(C1_overall_hospital_experience_score ~ B1_doctor_clear_answers + 
             B2_nurse_clear_answers + 
             B3_consistent_staff_answers + 
             B4_doctor_clear_communication + 
             B5_doctor_anxiety_counseling + 
             B6_nurse_anxiety_counseling +
             B8_respectful_treatment_by_staff + 
             B10_experienced_pain +
             B13_clear_medication_instructions + 
             B14_medication_side_effects_explained +
             B15_warning_signs_explained +
             age_category + 
             A2_gender + 
             length_of_stay_clean + 
             A14_other_chronic_disease + 
             A17_discharge_condition +
             A11_1_clinical_department_cleaned, data = data1_processed)

# Both-direction stepwise regression
both_model <- step(both_model, direction = "both", trace = 0)
```

```{r, eval = FALSE}
#model5
model5 <- lm(C1_overall_hospital_experience_score ~ 
               age_category + A2_gender +
             length_of_stay_clean + A14_other_chronic_disease + 
             A17_discharge_condition, data = data1_processed)

               
```

```{r}
#model6
model6 <- lm(C1_overall_hospital_experience_score ~ 
               A2_gender + 
               age_category + 
               A4_education_level +
               A5_marital_status +
               A6_living_situation + 
               A7_0_occupation_code + 
               A8_monthly_income + 
               A9_payment_method + 
               A10_hospital_treated + 
               A11_1_clinical_department_code + 
               A12_0_admission_reason_code + 
               length_of_stay_clean + 
               A14_other_chronic_disease +  
               A15_health_insurance + 
               A16_used_insurance_for_payment + 
               A17_discharge_condition + 
               A18_physical_health_perception + 
               A19_mental_health_perception + 
               C2_trust_hospital_quality + 
               C3_would_recommend_hospital + 
               C4_hospital_loyalty + 
               C5_intention_to_return, 
             data = data1_processed)
               
par(mfrow = c(2,2))
plot(model6)
```

```{r}
model7 <- lm(C1_overall_hospital_experience_score ~ 
               A2_gender + 
               A4_education_level +
               # A5_marital_status +
               # A6_living_situation + 
               A7_occupation_broad +
               A9_payment_method_group + 
               # A10_hospital_treated + 
               A12_0_admission_reason_fix + 
               length_of_stay_clean + 
               A16_used_insurance_for_payment 
               # A17_discharge_condition + 
               # A18_physical_health_perception + 
               # A19_mental_health_perception +
               # C2_trust_hospital_quality + 
               # C3_would_recommend_hospital + 
               # C4_hospital_loyalty + 
               # C5_intention_to_return
               , data = data1_processed)
               
par(mfrow = c(2,2))
plot(model7)
```

```{r}
x_var <- c("A2_gender",  
               "age_category",  
               "A4_education_level", 
               "A5_marital_status", 
               "A6_living_situation",  
               "A7_0_occupation_code",  
               "A8_monthly_income", 
               "A9_payment_method", 
               "A10_hospital_treated",  
               "A11_1_clinical_department_code", 
               "A12_0_admission_reason_code", 
               "length_of_stay_clean", 
               "A14_other_chronic_disease",  
               "A15_health_insurance", 
               "A16_used_insurance_for_payment", 
               "A17_discharge_condition", 
               "A18_physical_health_perception",  
               "A19_mental_health_perception", 
               "C2_trust_hospital_quality", 
               "C3_would_r3ecommend_hospital", 
               "C4_hospital_loyalty",
               "C5_intention_to_return") 

y_var <- "C1_overall_hospital_experience_score" 

results <- lapply(x_var, function(v) {
    f <- as.formula(paste(y_var, "~", v))
    tidy(lm(f, data = data1_processed)) %>%
        mutate(variable = v)
})

results_df <- bind_rows(results) 

results_clean <- results_df %>%
  filter(term != "(Intercept)") %>%
  transmute(
    variable,
    estimate = round(estimate, 3),
    std_error = round(std.error, 3),
    statistic = round(statistic, 3),
    p_value = round(p.value, 3)
  )

results_clean


```

```{r fix_var}
data1_processed <- data1_processed %>%
  mutate(
    A12_0_admission_reason_fix = case_when(
      A12_0_admission_reason_code %in% c("Dịch vụ sản khoa", "Điều trị hoá chất", "Khác") ~ "Khác",
      A12_0_admission_reason_code == "Điều trị bệnh mạn tính" ~ "Điều trị bệnh mạn tính",
      A12_0_admission_reason_code == "Điều trị đợt cấp của bệnh" ~ "Điều trị đợt cấp của bệnh",
      A12_0_admission_reason_code == "Nhập viện cấp cứu" ~ "Nhập viện cấp cứu",
      A12_0_admission_reason_code == "Phẫu thuật/thủ thuật" ~ "Phẫu thuật/thủ thuật",
      TRUE ~ NA_character_
    )
  )

data1_processed <- data1_processed %>%
  mutate (A9_payment_method_group = case_when(
    A9_payment_method %in% c("Được BHXH chi trả", "Tự chi trả được") ~ "Không gặp vấn đề với việc chi trả viện phí", 
    A9_payment_method %in% c("Phải vay mượn", "Vừa được BHXH chi trả và vừa vay mượn") ~ "Gặp khó khăn với việc chi trả viện phí", 
    TRUE ~ NA_character_))

```

```{r check_model_fix}
cooksD <- cooks.distance(model)
influential_points <- which(cooksD > (4/length(cooksD)))
influential_points

std_resid <- rstandard(model7)
outliers_resid <- which(abs(std_resid) > 2)   # Ngưỡng 2 hoặc 3
outliers_resid

leverage <- hatvalues(model7)
cutoff <- 2 * (length(coef(model7))) / nrow(data1_processed)
outliers_leverage <- which(leverage > cutoff)
outliers_leverage

p_load(car)
influenceIndexPlot(model7, id.n = 5)   # Vẽ các chỉ số ảnh hưởng
influencePlot(model7, id.n = 5)
```

```{r model_A}
model_A <- lm(C1_overall_hospital_experience_score ~ 
               A2_gender + 
               A4_education_level +
               # A5_marital_status +
               # A6_living_situation + 
               A7_occupation_broad +
               A9_payment_method_group + 
               # A10_hospital_treated + 
               A12_0_admission_reason_fix + 
               length_of_stay_clean 
               # A16_used_insurance_for_payment 
               # A17_discharge_condition + 
               # A18_physical_health_perception + 
               # A19_mental_health_perception +
               # C2_trust_hospital_quality + 
               # C3_would_recommend_hospital + 
               # C4_hospital_loyalty + 
               # C5_intention_to_return
               , data = data1_processed)

model_A_sensitivity <- lm(C1_overall_hospital_experience_score ~ 
               A2_gender + 
               A4_education_level +
               # A5_marital_status +
               # A6_living_situation + 
               A7_occupation_broad +
               A9_payment_method_group + 
               # A10_hospital_treated + 
               A12_0_admission_reason_fix + 
               length_of_stay_clean
               # A16_used_insurance_for_payment 
               # A17_discharge_condition + 
               # A18_physical_health_perception + 
               # A19_mental_health_perception +
               # C2_trust_hospital_quality + 
               # C3_would_recommend_hospital + 
               # C4_hospital_loyalty + 
               # C5_intention_to_return
               , data = data1_processed[-c(1463, 3201, 3229, 3248), ])
               
par(mfrow = c(2,2))
plot(model_A)
check_model(model_A)
check_model(model_A_sensitivity)
summary(model_A)
summary(model_A_sensitivity)
```

```{r model_B}

data1_processed$B10_1_staff_helped_pain_control <- fct_explicit_na(
  data1_processed$B10_1_staff_helped_pain_control, na_level = "Không áp dụng")

data1_processed$B14_medication_side_effects_explained <- fct_explicit_na(
  data1_processed$B14_medication_side_effects_explained, na_level = "Không áp dụng")

model_B <- lm(C1_overall_hospital_experience_score ~ 
                B1_doctor_clear_answers + 
                B2_nurse_clear_answers + 
                B3_consistent_staff_answers + 
                B4_doctor_clear_communication + 
                B5_doctor_anxiety_counseling + 
                B6_nurse_anxiety_counseling + 
                B7_want_treatment_decision_participation + 
                B8_respectful_treatment_by_staff +
                B9_shared_concerns_with_staff + 
                B10_1_staff_helped_pain_control +
                B11_family_communication_with_doctor + 
                B12_family_received_recovery_information + 
                B13_clear_medication_instructions + 
                B14_medication_side_effects_explained + 
                B15_warning_signs_explained
               , data = data1_processed)

model_B_sensitivity <- lm(C1_overall_hospital_experience_score ~ 
                B1_doctor_clear_answers + 
                B2_nurse_clear_answers + 
                B3_consistent_staff_answers + 
                B4_doctor_clear_communication + 
                B5_doctor_anxiety_counseling + 
                B6_nurse_anxiety_counseling + 
                B7_want_treatment_decision_participation + 
                B8_respectful_treatment_by_staff +
                B9_shared_concerns_with_staff + 
                B10_1_staff_helped_pain_control +
                B11_family_communication_with_doctor + 
                B12_family_received_recovery_information + 
                B13_clear_medication_instructions + 
                B14_medication_side_effects_explained + 
                B15_warning_signs_explained, 
                data = data1_processed[-c(1463, 3201, 3229, 3248), ])

par(mfrow = c(2,2))
plot(model_B)
check_model(model_B)
check_model(model_B_sensitivity)
summary(model_B)
summary(model_B_sensitivity)
```

```{r model_C}

```

```{r print_table_model}
model_A_sensitivity_table <-
  tbl_regression(
    model_A_sensitivity,
    exponentiate = FALSE,   # hoặc bỏ dòng này
    label = list(
      A2_gender ~ "Giới tính",
      A4_education_level ~ "Trình độ học vấn",
      A7_occupation_broad ~ "Nghề nghiệp",
      A9_payment_method_fix ~ "Khả năng thanh toán viện phí",
      A12_0_admission_reason_fix ~ "Lý do nhập viện",
      length_of_stay_clean ~ "Thời gian nằm viện",
      A16_used_insurance_for_payment ~ "Có sử dụng BHYT để thanh toán?"
    ),
    estimate_fun = function(x) style_sigfig(x, digits = 3),
    pvalue_fun   = function(x) style_pvalue(x, digits = 3)
  ) %>%
  bold_p(t = 0.05) %>%        # ✅ phiên bản bạn đang dùng dùng `t=`
  modify_header(
    label   = "**Biến**",
    estimate= "**β**",
    ci      = "**95% CI**",
    p.value = "**p-value**")

library(gtsummary)
library(flextable)
library(officer)

model_A_sensitivity_flex <- model_A_sensitivity_table %>%
  as_flex_table() %>%
  theme_vanilla() %>%
  # Header format
  bg(part = "header", bg = "#D9D9D9") %>%
  color(part = "header", color = "black") %>%
  bold(part = "header") %>%
  align(part = "header", align = "center") %>%
  # Body format
  align(
    j = c("estimate", "conf.low", "p.value"),
    align = "center", part = "body"
  ) %>%
  align(j = "label", align = "left", part = "body") %>%
  bg(
    i = seq(2, nrow(model_A_sensitivity_table$table_body), by = 2),
    bg = "#F2F2F2", part = "body"
  ) %>%
  width(j = "label", width = 2.8) %>%
  width(j = c("estimate", "conf.low", "p.value"), width = 1.0) %>%
  # Footer
  add_footer_lines(
    paste0(
      "β = Hệ số ước lượng; CI = Khoảng tin cậy 95%; N = ",
      nobs(model_A_sensitivity)
    )
  ) %>%
  fontsize(part = "footer", size = 9) %>%
  italic(part = "footer") %>%
  width(j = 1, width = 2.8) %>%
  width(j = 2, width = 1.0) %>% 
  width(j = 3, width = 1.5) %>%
  width(j = 4, width = 1.0)

model_A_sensitivity_flex

save_as_docx(model_A_sensitivity_flex,
             path = "model_A_sensitivity_table_2.docx")
```

```{r, include = FALSE}
knitr:: opts_chunk$set(echo = FALSE, warning = FALSE, mesage = FALSE, comment = "##", 
                       dpi = 4*72, fig.width = 8.5, fig.height = 4.5)
```

