---
title: "Hospital Survey Data Analysis"
author: "Đam Mê Nghiên Cứu"
date: "`r Sys.Date()`"
output:
  word_document:
  fig_caption: yes
  html_document: default
---

```{r Set_up, include = FALSE}
# Ẩn toàn bộ code + output của chính chunk này
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,  
  comment = "##",
  dpi = 600, 
  fig.width = 8.5, 
  fig.height = 4.5, 
  cache = FALSE)

# Nạp gói và theme, chặn mọi message khởi động
suppressPackageStartupMessages({
  if (!requireNamespace("pacman", quietly = TRUE)) install.packages("pacman")
  pacman::p_load(
    tidyverse, gtsummary, gt, flextable, officer, broom,
    performance, car, forcats, glue, janitor, here, 
    olsrr, pscl, DHARMa, MASS, pROC, scales, ResourceSelection)
  theme_gtsummary_journal(journal = "jama")})
```

```{r Prepare_data, include = FALSE}
# Chuẩn bị dữ liệu (nền)
# Import file làm sạch số liệu vào trong file phân tích số liệu
knitr::knit_child("prepare_raw_data.Rmd", quiet = TRUE)
```

```{r Flex_table_promt, echo = FALSE, include = FALSE}
style_flex_jama <- function(ft, caption = NULL, footer = NULL, zebra = TRUE){
  ft <- ft |>
    font(font = "Arial", part = "all") |>
    fontsize(size = 11, part = "all") |>
    bold(part = "header") |>
    border_remove() |>
    hline_top(part = "header", border = fp_border(color = "black", width = 2)) |>
    hline(part = "header",     border = fp_border(color = "black", width = 1)) |>
    hline_bottom(part = "body",border = fp_border(color = "black", width = 2)) |>
    align(align = "left", part = "all") |>
    autofit()
  if (!is.null(caption)) ft <- set_caption(ft, caption)
  if (!is.null(footer))  ft <- add_footer_lines(ft, values = footer)
  if (isTRUE(zebra)) {
    n_body <- nrow_part(ft, part = "body")
    if (n_body > 0) ft <- bg(ft, i = seq(1, n_body, by = 2), part = "body", bg = "#F8F9FA")
  }
  ft
}
```

```{r Table_1_A, echo = FALSE, results = "asis"}
# Table 1: Bảng mô tả biến số phần A
data1_processed <- data1_processed |>
  dplyr::mutate(
    A10_hospital_treated = forcats::fct_infreq(as.factor(A10_hospital_treated)),
    dplyr::across(
      c(age_category, A2_gender, A4_education_level, A5_marital_status,
        A6_living_situation, A7_occupation_broad, A8_monthly_income,
        A9_payment_method, A12_0_admission_reason_fix, length_of_stay_group,
        A14_other_chronic_disease, A15_health_insurance,
        A16_used_insurance_for_payment, A17_discharge_condition,
        A18_physical_health_perception, A19_mental_health_perception),
      ~ as.factor(.x)
    )
  )

table_1 <- data1_processed |>
  dplyr::select(
    age_category, A2_gender, A4_education_level, A5_marital_status,
    A6_living_situation, A7_occupation_broad, A8_monthly_income,
    A9_payment_method, A10_hospital_treated, A12_0_admission_reason_fix,
    length_of_stay_clean,
    A14_other_chronic_disease, A15_health_insurance,
    A16_used_insurance_for_payment, A17_discharge_condition,
    A18_physical_health_perception, A19_mental_health_perception
  ) |>
  gtsummary::tbl_summary(
    label = list(
      age_category ~ "Age Group (years)",
      A2_gender ~ "Gender",
      A4_education_level ~ "Education Level",
      A5_marital_status ~ "Marital Status",
      A6_living_situation ~ "Living Situation",
      A7_occupation_broad ~ "Occupation",
      A8_monthly_income ~ "Monthly Income",
      A9_payment_method ~ "Payment Method",
      A10_hospital_treated ~ "Hospital Treated",
      A12_0_admission_reason_fix ~ "Admission Reason",
      length_of_stay_clean ~ "Length of Stay (days)",
      A14_other_chronic_disease ~ "Other Chronic Disease",
      A15_health_insurance ~ "Health Insurance",
      A16_used_insurance_for_payment ~ "Used Insurance for Payment",
      A17_discharge_condition ~ "Discharge Condition",
      A18_physical_health_perception ~ "Physical Health Perception",
      A19_mental_health_perception ~ "Mental Health Perception"
    ),
    statistic = list(
      gtsummary::all_continuous() ~ "{median} ({p25}, {p75})",
      gtsummary::all_categorical() ~ "{n} ({p}%)"
    ),
    type = list(
      length_of_stay_clean ~ "continuous"
    ),
    missing_text = "Missing"
  ) |>
  gtsummary::bold_labels() |>
  gtsummary::modify_header(
    label  ~ "**Characteristic**",
    stat_0 ~ "**Overall**\nN = {N}"
  )
```

#Table 1 A: Describe Demographic Characteristic of Patients 
```{r Print_flex_table_1_A, echo = FALSE, results = "asis"}
final_table_1_A <- table_1 |>
gtsummary::as_flex_table() |>
flextable::font(font = "Arial", part = "all") |>
flextable::fontsize(size = 11, part = "all") |>
flextable::bold(part = "header") |>
flextable::border_remove() |>
flextable::hline_top(part = "header",
border = officer::fp_border(color = "black", width = 2)) |>
flextable::hline(part = "header",
border = officer::fp_border(color = "black", width = 1)) |>
flextable::hline_bottom(part = "body",
border = officer::fp_border(color = "black", width = 2)) |>
flextable::autofit() |>
flextable::set_caption("Table 1. Patient characteristics (overall sample)") |>
flextable::add_footer_lines(
"Data are median (IQR) for continuous variables and n (%) for categorical variables."
) |>
flextable::align(align = "left", part = "all")

n_body <- flextable::nrow_part(final_table_1_A, part = "body")
final_table_1_A <- flextable::bg(
final_table_1_A,
i = seq(1, n_body, by = 2), # 1,3,5,...
part = "body",
bg = "#F8F9FA"
)

final_table_1_A 
```

```{r Table_1_B, echo = FALSE, results = "asis"}
# Table_1_B: Bảng mô tả biến số liệu phần B
data1_processed <- data1_processed |>
  dplyr::mutate(
    dplyr::across(
      c(B1_doctor_clear_answers,
        B2_nurse_clear_answers,
        B3_consistent_staff_answers,
        B4_doctor_clear_communication,
        B5_doctor_anxiety_counseling,
        B6_nurse_anxiety_counseling,
        B7_want_treatment_decision_participation,
        B8_respectful_treatment_by_staff,
        B9_shared_concerns_with_staff,
        B10_experienced_pain,
        B10_1_staff_helped_pain_control,   # nhánh của B10 (chỉ hiện khi có đau)
        B11_family_communication_with_doctor,
        B12_family_received_recovery_information,
        B13_clear_medication_instructions,
        B14_medication_side_effects_explained, # nhánh của B13
        B15_warning_signs_explained),
      ~ as.factor(.x))
    ,
        B10_1_staff_helped_pain_control =
      forcats::fct_explicit_na(B10_1_staff_helped_pain_control, na_level = "Not applicable"),
    B14_medication_side_effects_explained =
      forcats::fct_explicit_na(B14_medication_side_effects_explained, na_level = "Not applicable"))

table_1_b <- data1_processed |>
  dplyr::select(
    B1_doctor_clear_answers,
    B2_nurse_clear_answers,
    B3_consistent_staff_answers,
    B4_doctor_clear_communication,
    B5_doctor_anxiety_counseling,
    B6_nurse_anxiety_counseling,
    B7_want_treatment_decision_participation,
    B8_respectful_treatment_by_staff,
    B9_shared_concerns_with_staff,
    B10_experienced_pain,
    B10_1_staff_helped_pain_control,          # có skip pattern
    B11_family_communication_with_doctor,
    B12_family_received_recovery_information,
    B13_clear_medication_instructions,
    B14_medication_side_effects_explained,    # có skip pattern
    B15_warning_signs_explained
  ) |>
  gtsummary::tbl_summary(
    label = list(
      B1_doctor_clear_answers ~ "B1. Doctor gave clear answers",
      B2_nurse_clear_answers ~ "B2. Nurse gave clear answers",
      B3_consistent_staff_answers ~ "B3. Staff gave consistent answers",
      B4_doctor_clear_communication ~ "B4. Doctor communicated clearly",
      B5_doctor_anxiety_counseling ~ "B5. Doctor addressed anxiety",
      B6_nurse_anxiety_counseling ~ "B6. Nurse addressed anxiety",
      B7_want_treatment_decision_participation ~ "B7. Wanted to join decisions",
      B8_respectful_treatment_by_staff ~ "B8. Treated respectfully",
      B9_shared_concerns_with_staff ~ "B9. Could share concerns",
      B10_experienced_pain ~ "B10. Experienced pain during stay",
      B10_1_staff_helped_pain_control ~ "B10.1 Staff helped with pain control",
      B11_family_communication_with_doctor ~ "B11. Family could talk to doctor",
      B12_family_received_recovery_information ~ "B12. Family got recovery info",
      B13_clear_medication_instructions ~ "B13. Clear med instructions",
      B14_medication_side_effects_explained ~ "B14. Side effects explained",
      B15_warning_signs_explained ~ "B15. Warning signs explained"
    ),
    statistic = list(
      gtsummary::all_categorical() ~ "{n} ({p}%)"
    ),
    missing = "no" # Ẩn Missing (vì đã thay NA = "Not applicable")
  ) |>
  gtsummary::bold_labels() |>
  gtsummary::modify_header(
    label  ~ "**Item (PPE-15)**",
    stat_0 ~ "**Overall**\nN = {N}"
  )
```

#Table 1 B: Describe PPE - 15 Questions Result
```{r Print_flex_table_1_B, echo = FALSE, results = "asis"}
final_table_1_B <- table_1_b |>
  gtsummary::as_flex_table() |>
  flextable::font(font = "Arial", part = "all") |>
  flextable::fontsize(size = 11, part = "all") |>
  flextable::bold(part = "header") |>
  flextable::border_remove() |>
  flextable::hline_top(part = "header",
                       border = officer::fp_border(color = "black", width = 2)) |>
  flextable::hline(part = "header",
                   border = officer::fp_border(color = "black", width = 1)) |>
  flextable::hline_bottom(part = "body",
                          border = officer::fp_border(color = "black", width = 2)) |>
  flextable::autofit() |>
  flextable::set_caption("Table B. Patient experience items (PPE-15)") |>
  flextable::add_footer_lines(
    "Values are n (%). Items B10.1 and B14 are skip-pattern questions; Missing not displayed."
  ) |>
  flextable::align(align = "left", part = "all")

final_table_1_B
```

#Figure 1: Patients Experience Score 
```{r Box_plot_C1, echo = FALSE, fig.cap = "Điểm trải nghiệm người bệnh nội trú"}
data1_processed <- data1_processed %>%
  mutate(C1_overall_hospital_experience_score = as.numeric(C1_overall_hospital_experience_score))

#Tạo biểu đồ boxplot cho câu C1
ggplot(data1_processed, aes(y = C1_overall_hospital_experience_score)) +
  geom_boxplot(
    fill = "#2C77BF",        # màu hộp
    color = "black",         # viền đen
    width = 0.3, 
    outlier.shape = 21,
    outlier.fill = "#F8F9FA"
  ) +
  labs(
    title = "Điểm trải nghiệm người bệnh nội trú",
    y = "Điểm trải nghiệm (0 – 10)",
    x = NULL
  ) +
  scale_y_continuous(
    breaks = 0:10,
    limits = c(-0.5, 10.5),
    expand = expansion(mult = c(0, 0.02))
  ) +
  theme_minimal(base_family = "Arial") +
  theme(
    plot.title = element_text(face = "bold", size = 13, hjust = 0.5),
    axis.title.y = element_text(size = 11, face = "bold"),
    axis.text = element_text(size = 10),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank()
  )

```

```{r Table_1_C2-C5, echo = FALSE, results = "asis"}
#Bảng mô tả Phần C từ câu C2 đến C5
tbl_C2_C5 <- data1_processed %>%
  dplyr::mutate(
    dplyr::across(
      c(C2_trust_hospital_quality, 
        C3_would_recommend_hospital, 
        C4_hospital_loyalty,
        C5_intention_to_return),
      ~ as.factor(.x)
    )
  ) %>%
  dplyr::select(
    C2_trust_hospital_quality, 
    C3_would_recommend_hospital, 
    C4_hospital_loyalty,
    C5_intention_to_return
  ) %>%
  gtsummary::tbl_summary(
    label = list(
      C2_trust_hospital_quality ~ "Trust hospital quality",
      C3_would_recommend_hospital ~ "Would recommend hospital or not",
      C4_hospital_loyalty ~ "Hospital loyalty",
      C5_intention_to_return ~ "Intention to return"
    ),
    statistic = list(gtsummary::all_categorical() ~ "{n} ({p}%)"),
    missing = "no"
  ) %>%
  gtsummary::bold_labels() %>%
  gtsummary::modify_header(
    label  ~ "**Item (C2–C5)**",
    stat_0 ~ "**Overall**\nN = {N}"
  )
```

#Table 1 C2 - C5: Hospital Loyaty
```{r Print_flex_table_1_C2-C5, echo = FALSE, results = "asis"}
flex_table_C2_C5 <- tbl_C2_C5 |>
  gtsummary::as_flex_table() |>
  flextable::font(font = "Arial", part = "all") |>
  flextable::fontsize(size = 11, part = "all") |>
  flextable::bold(part = "header") |>
  flextable::border_remove() |>
  flextable::hline_top(part = "header",
                       border = officer::fp_border(color = "black", width = 2)) |>
  flextable::hline(part = "header",
                   border = officer::fp_border(color = "black", width = 1)) |>
  flextable::hline_bottom(part = "body",
                          border = officer::fp_border(color = "black", width = 2)) |>
  flextable::autofit() |>
  flextable::set_caption("Table C2 - C5: Hospital Loyalty") |>
  flextable::add_footer_lines(
    "Values are n (%)"
  ) |>
  flextable::align(align = "left", part = "all")

flex_table_C2_C5
```

```{r Table_1_C6, echo = FALSE, results = "asis"}
#Gắn ID cho bệnh nhân
data1_processed <- data1_processed %>%
  dplyr::mutate(resp_id = dplyr::row_number())

# 4.1. Danh mục lựa chọn chính thức (chuẩn hoá)
c6_official <- c(
  "Chất lượng dịch vụ",
  "Chi phí hợp lý",
  "Gần nơi sinh sống",
  "Sự chuyên nghiệp của nhân viên y tế",
  "Tôi không có lựa chọn khác"
)

# 4.2. Tách đa lựa chọn thành dạng dài (long)
c6_long <- data1_processed %>%
  dplyr::select(resp_id, C6_return_reason_text) %>%     # thay tên biến nếu khác
  dplyr::mutate(C6_return_reason_text = coalesce(C6_return_reason_text, "")) %>%
  separate_rows(C6_return_reason_text, sep = "[,;]+\\s*") %>%  # tách theo dấu phẩy/chấm phẩy
  mutate(choice_raw = str_squish(C6_return_reason_text)) %>%
  filter(choice_raw != "") %>%
  mutate(choice_group = if_else(choice_raw %in% c6_official, choice_raw, "Khác")) %>%
  distinct(resp_id, choice_group)   # mỗi người–mỗi nhóm lý do chỉ tính 1 lần

# 4.3. Mẫu số: số người có trả lời C6 (ít nhất một lựa chọn)
n_resp_c6 <- c6_long %>% distinct(resp_id) %>% nrow()
n_total   <- nrow(data1_processed)  # nếu muốn % trên toàn bộ mẫu

# 4.4. Bảng tần suất & tỷ lệ
tab_C6 <- c6_long %>%
  count(choice_group, name = "n") %>%
  mutate(
    percent_of_respondents = round(100 * n / n_resp_c6, 1),
    percent_of_total       = round(100 * n / n_total, 1)
  ) %>%
  arrange(desc(n))

# 4.5. (tuỳ chọn) liệt kê các phương án “Khác” phổ biến
tab_C6_other <- data1_processed %>%
  dplyr::select(resp_id, C6_return_reason_text) %>%
  dplyr::mutate(C6_return_reason_text = coalesce(C6_return_reason_text, "")) %>%
  separate_rows(C6_return_reason_text, sep = "[,;]+\\s*") %>%
  mutate(choice_raw = str_squish(C6_return_reason_text)) %>%
  filter(choice_raw != "", !(choice_raw %in% c6_official)) %>%
  count(choice_raw, sort = TRUE, name = "n")
```

#Table 1 C6: Reasons to return to the hospital
```{r Print_Table_1_C6, echo = FALSE, results = "asis"}
flex_table_1_C6 <- tab_C6 %>%
  dplyr::mutate(
    `Reason` = choice_group,
    `n` = n,
    `% of respondents` = percent_of_respondents,
    `% of total`       = percent_of_total
  ) %>%
  dplyr::select(`Reason`, n, `% of respondents`, `% of total`) %>%
  flextable::flextable() %>%
  flextable::font(font = "Arial", part = "all") %>%
  flextable::fontsize(size = 11, part = "all") %>%
  flextable::bold(part = "header") %>%
  flextable::autofit() %>%
  flextable::set_caption("Reasons to return to the hospital") %>%
  flextable::add_footer_lines(
    values = paste0(
      "Percent of respondents uses N = ", n_resp_c6,
      ". Items are multi-response. ‘Other’ aggregates non-listed reasons."
    )
  )

flex_table_1_C6

# flex_table_1_C6_other <- tab_C6_other %>%
#   dplyr::mutate(
#     Reason = choice_raw,
#     n = n,
#     `% of respondents` = round(100 * n / n_resp_c6, 1),
#     `% of total` = round(100 * n / n_total, 1)
#   ) %>%
#   dplyr::select(Reason, n, `% of respondents`, `% of total`) %>%
#   flextable::flextable() %>%
#   flextable::font(font = "Arial", part = "all") %>%
#   flextable::fontsize(size = 11, part = "all") %>%
#   flextable::bold(part = "header") %>%
#   flextable::autofit() %>%
#   flextable::set_caption("Other reasons to return to the hospital") %>%
#   flextable::add_footer_lines(
#     values = paste0(
#       "Percent of respondents uses N = ", n_resp_c6,
#       ". Items are multi-response; ‘Other’ aggregates non-listed reasons."
#     )
#   )
```

```{r Table_2_Model_A_full, echo = FALSE, results = "asis"}
#Model A gồm tất cả các biến nhân khẩu học trong phần A
model_full_raw <- lm(C1_overall_hospital_experience_score ~ 
                       A2_gender + 
                       age_category + 
                       A4_education_level + 
                       A5_marital_status + 
                       A6_living_situation + 
                       A7_0_occupation_code + 
                       A8_monthly_income + 
                       A9_payment_method + 
                       A10_hospital_treated + 
                       A12_0_admission_reason_code + 
                       length_of_stay_clean + 
                       A14_other_chronic_disease + 
                       A15_health_insurance + 
                       A16_used_insurance_for_payment + 
                       A17_discharge_condition + 
                       A18_physical_health_perception + 
                       A19_mental_health_perception, 
                     data = data1_processed)
##Adj R^2 của mô hình này là 0.2250195

model_2_A_full_grp <- lm(C1_overall_hospital_experience_score ~ 
               A2_gender + 
               age_category + 
               A4_education_level +
               A5_marital_status +
               A6_living_situation + 
               A7_occupation_broad + 
               A8_monthly_income + 
               A9_payment_method + 
               A10_hospital_treated + 
               A12_0_admission_reason_fix + 
               length_of_stay_group + 
               A14_other_chronic_disease +  
               A15_health_insurance + 
               A16_used_insurance_for_payment + 
               A17_discharge_condition + 
               A18_physical_health_perception + 
               A19_mental_health_perception, 
             data = data1_processed)
##Adj R^2 của mô hình này là 0.2278061

model_2_A_reduced <- lm(C1_overall_hospital_experience_score ~ 
               A2_gender + 
               A4_education_level +
               # A5_marital_status +
               # A6_living_situation + 
               A7_occupation_broad +
               A9_payment_method_group + 
               # A10_hospital_treated + 
               A12_0_admission_reason_fix + 
               length_of_stay_clean + 
               A16_used_insurance_for_payment 
               # A17_discharge_condition + 
               # A18_physical_health_perception + 
               # A19_mental_health_perception +
               # C2_trust_hospital_quality + 
               # C3_would_recommend_hospital + 
               # C4_hospital_loyalty + 
               # C5_intention_to_return
               , data = data1_processed)
##Adj R^2 của mô hình này là 0.05603

model_2_A_step <- lm(C1_overall_hospital_experience_score ~ 
               A2_gender + 
               # age_category + 
               # A4_education_level +
               A5_marital_status +
               # A6_living_situation +
               A7_occupation_broad + 
               A8_monthly_income +
               A9_payment_method + 
               A10_hospital_treated + 
               A12_0_admission_reason_fix + 
               length_of_stay_group + 
               # A14_other_chronic_disease +
               A15_health_insurance + 
               A16_used_insurance_for_payment + 
               A17_discharge_condition + 
               # A18_physical_health_perception + 
               A19_mental_health_perception, 
             data = data1_processed)
##Adj R^2 của mô hình này là 0.2273, AIC thấp nhất 179,84

#Tìm mô hình có Adj R^2 tối ưu: best_subset <- ols_step_best_subset(model_2_A_full_grp)
```

#Model Linear Regression A: Demographic Characteristics of patients
```{r Prints_model_A, echo = FALSE, results = "asis"}
table_2_A_full_grp <- gtsummary::tbl_regression(
  model_2_A_full_grp,
  intercept = FALSE,      # không hiển thị hệ số chặn
  estimate_fun = ~ style_sigfig(.x, digits = 2)  # làm tròn 2 chữ số có ý nghĩa
) |>
  bold_labels() |>
  modify_caption("**Table B. Multivariable linear regression for patient experience (PPE-15, Section B)**")

flex_table_2_A_full_grp <- as_flex_table(table_2_A_full_grp) |>
  style_flex_jama(
    caption = "Multivariable linear regression for Demographic Characteristics of patients (Full)",
    footer  = "Values are β coefficients (95% CI) from a linear regression model. Outcome: overall inpatient experience score (C1)."
  )

flex_table_2_A_full_grp

table_2_A_reduced <- gtsummary::tbl_regression(
  model_2_A_reduced,
  intercept = FALSE,      # không hiển thị hệ số chặn
  estimate_fun = ~ style_sigfig(.x, digits = 2)  # làm tròn 2 chữ số có ý nghĩa
) |>
  bold_labels() |>
  modify_caption("**Table B. Multivariable linear regression for patient experience (PPE-15, Section B)**")

flex_table_2_A_reduced  <- as_flex_table(table_2_A_reduced) |>
  style_flex_jama(
    caption = "Multivariable linear regression for Demographic Characteristics of patients (Reduced)",
    footer  = "Values are β coefficients (95% CI) from a linear regression model. Outcome: overall inpatient experience score (C1)."
  )

flex_table_2_A_reduced

table_2_A_step <- gtsummary::tbl_regression(
  model_2_A_step,
  intercept = FALSE,      # không hiển thị hệ số chặn
  estimate_fun = ~ style_sigfig(.x, digits = 2)  # làm tròn 2 chữ số có ý nghĩa
) |>
  bold_labels() |>
  modify_caption("**Table B. Multivariable linear regression for patient experience (PPE-15, Section B)**")

flex_table_2_A_step <- as_flex_table(table_2_A_step) |>
  style_flex_jama(
    caption = "Multivariable linear regression for Demographic Characteristics of patients (Stepped)",
    footer  = "Values are β coefficients (95% CI) from a linear regression model. Outcome: overall inpatient experience score (C1)."
  )

flex_table_2_A_step
```

#Comparission 3 model linear 
```{r Comparission_table_Model_2_A, echo = FALSE, results = "asis"}
get_model_strength <- function(model, name, data, type = c("lm","glm")) {
  type <- match.arg(type)
  if (type == "lm") {
    sm <- summary(model)
    perf <- performance::model_performance(model)
    tibble(
      Model = name,
      Type = "Linear",
      R2_or_Nagelkerke = round(sm$r.squared, 3),
      Adj_R2_or_McFadden = round(sm$adj.r.squared, 3),
      AIC = round(AIC(model), 2),
      RMSE_or_AUC = round(perf$RMSE, 3)
    )
  } else {
    pr2 <- pscl::pR2(model)
    roc_obj <- tryCatch(
      pROC::roc(data$c1_overall_experience_binary, fitted(model), quiet = TRUE),
      error = function(e) NULL
    )
    auc_val <- if (!is.null(roc_obj)) as.numeric(pROC::auc(roc_obj)) else NA
    tibble(
      Model = name,
      Type = "Logistic",
      R2_or_Nagelkerke = round(pr2["r2CU"], 3),       # Nagelkerke
      Adj_R2_or_McFadden = round(pr2["McFadden"], 3), # McFadden
      AIC = round(AIC(model), 2),
      RMSE_or_AUC = round(auc_val, 3)
    )
  }
}

results_strength <- bind_rows(
  get_model_strength(model_full_raw,       "Model A: Raw (all variables)", data1_processed, type = "lm"),
  get_model_strength(model_2_A_full_grp,   "Model B: Grouped (full)",      data1_processed, type = "lm"),
  get_model_strength(model_2_A_reduced,    "Model C: Reduced (manual)",    data1_processed, type = "lm"),
  get_model_strength(model_2_A_step,       "Model D: Stepped (stepwise)", data1_processed, type = "lm")
)

results_strength <- results_strength %>%
  rename(
    `Model type` = Type,
    `R² / Nagelkerke R²` = R2_or_Nagelkerke,
    `Adj R² / McFadden R²` = Adj_R2_or_McFadden,
    `AIC` = AIC,
    `RMSE / AUC` = RMSE_or_AUC
  )

ft_strength <- flextable(results_strength) %>%
  font(font = "Arial", part = "all") %>%
  fontsize(size = 10, part = "all") %>%
  bold(part = "header") %>%
  align(part = "all", align = "center") %>%
  align(j = "Model", align = "left", part = "all") %>%
  autofit() %>%
  set_caption("Comparison of model strength across four regression models") %>%
  add_footer_lines(
    "Linear models report R², Adjusted R², and RMSE. The logistic model reports Nagelkerke R², McFadden R², and AUC."
  ) %>%
  bg(i = seq(1, nrow(results_strength), 2), bg = "#F8F9FA", part = "body")

ft_strength
```

```{r Table_2_Model_B, echo = FALSE, results = "asis"}
model_2_B_full <- lm(C1_overall_hospital_experience_score ~ 
                       B1_doctor_clear_answers + 
                       B2_nurse_clear_answers + 
                       B3_consistent_staff_answers + 
                       B4_doctor_clear_communication + 
                       B5_doctor_anxiety_counseling + 
                       B6_nurse_anxiety_counseling + 
                       B7_want_treatment_decision_participation + 
                       B8_respectful_treatment_by_staff + 
                       B9_shared_concerns_with_staff + 
                       B10_1_staff_helped_pain_control + 
                       B11_family_communication_with_doctor + 
                       B12_family_received_recovery_information + 
                       B13_clear_medication_instructions + 
                       B14_medication_side_effects_explained + 
                       B15_warning_signs_explained, 
                     data = data1_processed)
##Adj R^2 của mô hình này là 0.3332415
```

#Model Linear Regression B: PPE - 15 Questions 
```{r Prints_table_Model_2_B, echo = FALSE, results = "asis"}
table_2_b_full <- gtsummary::tbl_regression(
  model_2_B_full,
  intercept = FALSE,      # không hiển thị hệ số chặn
  estimate_fun = ~ style_sigfig(.x, digits = 2)  # làm tròn 2 chữ số có ý nghĩa
) |>
  bold_labels() |>
  modify_caption("**Table B. Multivariable linear regression for patient experience (PPE-15, Section B)**")

flex_table_2_B_full <- as_flex_table(table_2_b_full) |>
  style_flex_jama(
    caption = "Multivariable linear regression for PPE-15 Questions",
    footer  = "Values are β coefficients (95% CI) from a linear regression model. Outcome: overall inpatient experience score (C1)."
  )

flex_table_2_B_full
```

```{r Table_2_A_Logistic, echo = FALSE, results = "asis"}
data1_processed <- data1_processed %>% 
  mutate(c1_overall_experience_binary_num = ifelse(c1_overall_experience_binary == "Positive", 1, 0))

model_2_A_full_grp_logistic <- glm(c1_overall_experience_binary ~ 
               A2_gender + 
               age_category + 
               A4_education_level +
               A5_marital_status +
               A6_living_situation + 
               A7_occupation_broad + 
               A8_monthly_income + 
               A9_payment_method + 
               A10_hospital_treated + 
               A12_0_admission_reason_fix + 
               length_of_stay_group + 
               A14_other_chronic_disease +  
               A15_health_insurance + 
               A16_used_insurance_for_payment + 
               A17_discharge_condition + 
               A18_physical_health_perception + 
               A19_mental_health_perception, 
             data = data1_processed, 
             family = binomial)

model_2_A_full_grp_logistic_end <- glm(c1_overall_experience_binary ~ 
               A2_gender + 
               age_category + 
               # A4_education_level +
               A5_marital_status +
               # A6_living_situation + 
               A7_occupation_broad + 
               # A8_monthly_income + 
               A9_payment_method + 
               A10_hospital_treated + 
               A12_0_admission_reason_fix + 
               length_of_stay_group + 
               # A14_other_chronic_disease +  
               A15_health_insurance + 
               A16_used_insurance_for_payment + 
               A17_discharge_condition + 
               # A18_physical_health_perception + 
               A19_mental_health_perception, 
             data = data1_processed, 
             family = binomial)

model_2_A_full__grp_logistic_fix <- stepAIC (model_2_A_full_grp_logistic, direction = "both", trace = FALSE)
```

#Model A Logistic Regression: Demographic Characteristics of patients
```{r Print_table_2_modelB, echo = FALSE, results = "asis"}
tbl_A_logistic_full <- tbl_regression(
  model_2_A_full_grp_logistic,
  exponentiate = TRUE, # OR
  intercept = FALSE
) |>
  bold_labels() |>
  modify_caption("**Multivariable logistic regression (Full grouped)**")

flex_table_A_logistic_full <- as_flex_table(tbl_A_logistic_full) |>
  style_flex_jama(
    caption = "Multivariable logistic regression (Full grouped)",
    footer  = "Values are Odds Ratio (95% CI)."
  )

flex_table_A_logistic_full

tbl_A_logistic_end <- tbl_regression(
  model_2_A_full_grp_logistic_end,
  exponentiate = TRUE,
  intercept = FALSE
) |>
  bold_labels() |>
  modify_caption("**Multivariable logistic regression (Reduced, manual)**")

flex_table_A_logistic_end <- as_flex_table(tbl_A_logistic_end) |>
  style_flex_jama(
    caption = "Multivariable logistic regression (Reduced, manual)",
    footer  = "Values are Odds Ratio (95% CI)."
  )

flex_table_A_logistic_end

tbl_A_logistic_fix <- tbl_regression(
  model_2_A_full__grp_logistic_fix,
  exponentiate = TRUE,
  intercept = FALSE
) |>
  bold_labels() |>
  modify_caption("**Multivariable logistic regression (StepAIC both)**")

flex_table_A_logistic_fix <- as_flex_table(tbl_A_logistic_fix) |>
  style_flex_jama(
    caption = "Multivariable logistic regression (StepAIC both)",
    footer  = "Values are Odds Ratio (95% CI)."
  )

flex_table_A_logistic_fix
```

#Comparision Model B
```{r Comparision_assumption_table_model_logistic, echo = FALSE, results = "asis"}
get_metrics <- function(model, model_name, data, y_num, g = 10) {
  pr2 <- pscl::pR2(model)
  aic <- AIC(model)
  roc_obj <- pROC::roc(response = data[[y_num]], predictor = fitted(model), quiet = TRUE)
  auc_val <- as.numeric(pROC::auc(roc_obj))
  acc <- mean(ifelse(fitted(model) >= 0.5, 1, 0) == data[[y_num]])  # cut 0.5
  hl <- tryCatch(ResourceSelection::hoslem.test(data[[y_num]], fitted(model), g = g),
                 error = function(e) NULL)
  tibble(
    Model = model_name,
    AIC = aic,
    McFadden_R2   = unname(pr2["McFadden"]),
    CoxSnell_R2   = unname(pr2["r2ML"]),
    Nagelkerke_R2 = unname(pr2["r2CU"]),
    AUC = auc_val,
    Accuracy_0_5 = acc,
    HL_p = if (!is.null(hl)) hl$p.value else NA_real_
  )
}

metrics_df <- bind_rows(
  get_metrics(model_2_A_full_grp_logistic,      "Full grouped",    data1_processed, "c1_overall_experience_binary_num", g = 10),
  get_metrics(model_2_A_full_grp_logistic_end,  "Reduced manual",  data1_processed, "c1_overall_experience_binary_num", g = 10),
  get_metrics(model_2_A_full__grp_logistic_fix, "StepAIC both",    data1_processed, "c1_overall_experience_binary_num", g = 10)
) %>%
  mutate(
    AIC = round(AIC, 1),
    McFadden_R2   = round(McFadden_R2, 3),
    CoxSnell_R2   = round(CoxSnell_R2, 3),
    Nagelkerke_R2 = round(Nagelkerke_R2, 3),
    AUC = round(AUC, 3),
    Accuracy_0_5 = percent(Accuracy_0_5, accuracy = 0.1),
    HL_p = ifelse(is.na(HL_p), NA, formatC(HL_p, digits = 3, format = "f"))
  )

ft_metrics <- flextable(metrics_df) %>%
  font(font = "Arial", part = "all") %>%
  fontsize(size = 10, part = "all") %>%
  bold(part = "header") %>%
  align(part = "all", align = "center") %>%
  align(j = "Model", align = "left", part = "all") %>%
  autofit() %>%
  set_caption("Model comparison (Logistic regression)") %>%
  add_footer_lines("R² are pseudo-R²; HL_p: Hosmer–Lemeshow p-value with g=10; Accuracy cutoff = 0.5.") %>%
  bg(i = seq(1, nrow(metrics_df), 2), bg = "#F8F9FA", part = "body")

ft_metrics
```




